Figures

### 2018-03-23 scripts/analysis.Rmd
add table captions
rename table chunks, convert chl units
explore alternative field abbrevations
reize, rescale plots, suppress warnings

```{r table_2, echo=FALSE, fig.cap="Table 2"}

@@

```{r table_3, echo=FALSE, fig.cap="Table 3"}

@@

```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data."}

@@

```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the hierarchical model posteriors relative to raw data. Dark lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 1)", fig.height=8.4}

@@

```{r table_1, echo=FALSE, fig.cap="Table 1"}

>>>>

```{r lake_characteristics_table, echo=FALSE, results='asis'}

@@

```{r cor_mat_table, echo=FALSE, results='asis'}

@@

```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE}

@@

```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the hierarchical model posteriors relative to raw data. Dark lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 1)", fig.height=8.4, warning=FALSE}

@@

```{r model_results_table, echo=FALSE, results='asis'}
